A Trio of 40 to 50 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-04-06 papers/ms.tex
update Li6708 analysis
Mostly wrangling the literature, and reminding myself that the
uncertainties on the M-dwarfs from Randich+18 make no sense, as do their
lack of upper limits.  (Though the earlier Randich+01 work seems fine).
Adding the Tuc-Hor Kraus+14 sample is a good sanity check.
See simultaneous commits at `timmy`.

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 August 16 and 2021 October 25.  The acquisition
and analysis followed the standard reduction techniques of the
California Planet Survey \citep{howard_cps_2010}.  We derived the
stellar parameters ($T_{\rm eff}, \log g, R_\star$) using
\texttt{SpecMatch-Emp} \citep{yee_SM_2017}, which yielded values in
$<1$-$\sigma$ agreement with those from the cluster-isochrone
approach.  This approach also yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.
Using the broadened synthetic templates from \texttt{SpecMatch-Synth}
\citep{petigura_cksi_2017}, we found $v\sin i = 9.3 \pm 1.0\,\mkms$.
The systemic radial velocity at the two sequence epochs was $-9.1 \pm
1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$ respectively.  To infer the
equivalent width of the Li\,\textsc{I} 6708\,\AA\ doublet, we followed
the procedure described by \citet{bouma_2021_ngc2516}.  This yielded a
strong detection: ${\rm EW}_{\rm Li} = 126^{+8}_{-4}$\,m\AA, with
values consistent at $<1$-$\sigma$ between the two epochs.   The
quoted value does not correct for the Fe\,\textsc{I} blend at
6707.44\AA.

@@

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present in the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep{kiman_calibration_2021}.  At $\approx$M0V, if
the secondary were in older than $\approx 500\,{\rm Myr}$, it would be
more common for its H$\alpha$ component to be observed in absorption
\citep[][Figure~4]{kiman_calibration_2021}.  H$\alpha$ emission in
late K-dwarfs is rarer still. Based on the data from K.~Rocio et al's
analysis\footnote{Available at
\url{https://zenodo.org/record/4659293\#.YkuKh27MKDV}}, a $\approx$K6V
star should be emitting in H$\alpha$ at 40\,Myr, but not typically
past $\approx200\,{\rm Myr}$.  This presents a fairly direct test for
the star's age.

>>>>

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 August 16 and 2021 October 25.  The acquisition
and analysis followed the standard reduction techniques of the
California Planet Survey \citep{howard_cps_2010}.  We derived the
stellar parameters ($T_{\rm eff}, \log g, R_\star$) using
\texttt{SpecMatch-Emp} \citep{yee_SM_2017}, which yielded values in
$<1$-$\sigma$ agreement with those from the cluster-isochrone
approach.  This approach also yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.
Using the broadened synthetic templates from \texttt{SpecMatch-Synth}
\citep{petigura_cksi_2017}, we found $v\sin i = 9.3 \pm 1.0\,\mkms$.
The systemic radial velocity at the two sequence epochs was $-9.1 \pm
1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$ respectively.  To infer the
equivalent width of the Li\,\textsc{I} 6708\,\AA\ doublet, we followed
the procedure described by \citet{bouma_2021_ngc2516}.  This yielded a
strong detection: ${\rm EW}_{\rm Li} = 126^{+8}_{-4}$\,m\AA, with
values consistent at $<1$-$\sigma$ between the two epochs.   The
quoted value does not correct for the Fe\,\textsc{I} blend at
6707.44\AA, because HIRES has sufficient resolution to resolve the two
features.

@@

% Randich+01: Li starts to become upper limits around K8V, V-I=1.6.
% Around K6V, V-I=1.4, ~100mA seen, but few stars in this region!

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present in the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep[{\it e.g.},][]{kiman_calibration_2021}.  For
the $\approx$K6V primary, H$\alpha$ emission is also expected based on
previous spectroscopic studies of the Pleiades, IC~2602, and IC~2391
\citep[{\it e.g.},][their Figure~8]{stauffer_rotational_1997}.  Based
on the data from K.~Rocio et al's analysis\footnote{Available at
\url{https://zenodo.org/record/4659293\#.YkuKh27MKDV}}, a $\approx$K6V
star should be emitting in H$\alpha$ at 40\,Myr, but not typically
past $\approx200\,{\rm Myr}$.  This presents a fairly direct test for
the star's age.
